2nd_draft

### 2020-03-19 src/2nd_draft.Rmd
assigned more

boxplot(mspe.la, 
        mspe.ri,
        mspe.reduced, 
        mspe.f, 
        names = c("LASSO", "Ridge", 
                  "Reduced", "Full"), 
        col = c("steelblue","gray80", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Prediction Power",
        ylab = expression(hat(MSPE)))
```

@@

write.csv(assessment_2020.final, "../Data/Assessment/assessment_2020.final")
write.csv(b, "../Data/assessment_2020.csv")
```
##_______________________________________

## Conclusion

@@

All fitted linear model were able to make accurate prediction based on means squared error, but there is still a very high chance that our model is overfitted. For our next report, we are going to use cross-validation to reduce the effect of overfitting.

>>>>

boxplot(mspe.la, 
        mspe.ri,
        mspe.reduced, 
        mspe.f, 
        names = c("LASSO", "Ridge", 
                  "Reduced", "Full"), 
        col = c("steelblue","gray80", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Prediction Power",
        ylab = expression(hat(MSPE)))
```
##_______________________________________

@@

write.csv(assessment_2020.final, "../Data/Assessment/assessment_2020.final")
write.csv(b, "../Data/assessment_2020.csv")
```

##_____________________________
## TODO: delete pct change part, add prediction based on our chosen model (Peter)
## Conclusion

@@

All fitted linear model were able to make accurate prediction based on means squared error, but there is still a very high chance that our model is overfitted. For our next report, we are going to use cross-validation to reduce the effect of overfitting. 
##_______________________________
